### 2016-12-01 paper/chapters/overview.tex
add citation to deep latent gaussian
rewritten overview for VAE

\paragraph{Variational Autoencoders\cite{vae:2013}}
\label{par:overview_vae}
Variational Autoencoders (VAE) use two networks called encoder and decoder where the encoder transform the given data into a latent space and the decoder translates this latent space back into the data space.
The input and output space are usually high-dimensional data spaces, for example images while the latent space is low-dimensional in comparison.
Like other autoencoders, VAEs try to reconstruct the input data using the latent variables as closely as possible.
But in addition to regular autoencoders encourages the VAE the latent space to match a specific probability distribution.
This encouragement is done using a variational lower bound on the distribution output by the encoder network.

>>>>

\paragraph{Variational Autoencoders (VAE) \cite{vae:2013}\cite{rezende:2014}}
\label{par:overview_vae}
Variational Autoencoders (VAE) use two networks which are trained jointly using approximated learned inference.
The objective function is aimed at building a reasonable simple latent space approximating the intractable posterior distribution using variational inference.
It consists of the recognition and inference network which can be understood in the autoencoder jargon as probabilistic encoder and decoder.
Using variational bayesian methods the intractable posterior distribution can be approximated and learned using backpropagation and gradient-based methods.

%But in addition to regular autoencoders encourages the VAE the latent space to match a specific probability distribution.
%This encouragement is done using a variational lower bound on the distribution output by the encoder network.
